The Forward March of Categorical Tolerance in the United States?

### 2024-05-20 analysis.qmd
just do it

>>>>

```{r}
  dat.g <- reg.dat[, c("id", "Classical", "Country", "Disco",
                            "Jazz", "Musicals", "Pop", "R_and_B",
                            "Rap", "Reggae", "Rock", "EDM", "Metal")] %>% 
    pivot_longer(
      cols = c(2:13),
      names_to = "genre",
      values_to = "Dislike"
    ) 
  t <- round(table(dat.g$genre, dat.g$Dislike)/nrow(reg.dat), 2) * 100
  t.w <- left_join(dat.g, reg.dat[, c("id", "weight")])
  t.w <- round(wtd.table(t.w$genre, t.w$Dislike, weights = t.w$weight)/nrow(reg.dat), 2) * 100
  t <- data.frame(d = t[, 2], wd = t.w[, 2]) %>% 
    kbl(caption = "", format = "html", align = "c", 
        col.names = c("Unweighted", "Weighted")) %>% 
          kable_classic_2(full_width = F, 
          html_font = "Garamond", font_size = 20) %>% 
          pack_rows("% Disliked", 1, 12) %>% 
          save_kable(here("Tabs", "desc-tab3.html"))

```
